Transcriptomic responses to diet quality and viral infection in Apis mellifera

### 2018-11-15 Manuscript/Text/manuscript.tex
Additional file 20

>>>>

  \subsection*{Additional file 20 --- Tables listing DEGs for contrasts.}
    \textbf{Table 1:} IDs of 1,914 DEGs in our diet main effect.
    \textbf{Table 2:} IDs of 43 DEGs in our virus main effect.
    \textbf{Table 3:} IDs of 178 DEGs in our NR versus VR contrast.
    \textbf{Table 4:} IDs of 376 DEGs in our VC versus VR contrast.
    \textbf{Table 5:} IDs of 774 DEGs in our NC versus VR contrast.
    \textbf{Table 6:} IDs of 955 DEGs in our VC versus NR contrast. 
    \textbf{Table 7:} IDs of 941 DEGs in our NC versus NR contrast. 
    \textbf{Table 8:} IDs of 125 resistance candidate genes.
    \textbf{Table 9:} IDs of 122 tolerance candidate genes. (XLS).
